Modelling BCG vaccination in the UK

### 2019-07-04 rmds/04-tb-epi-england.Rmd
updated figure captions

```{r plot-detection-not, fig.cap = "a.) and .b) show notifications over time by date of notification in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases notified in a given month for each year, with some evidence of a seasonal trend. d.) Shows the proportion of cases notified on a given day for each month, there is little evidence of between day variation in cases notified."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-not.png")
```

@@

```{r plot-detection-sympton, fig.cap = "a.) and .b) show notifications over time by date of symptom onset in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases notified in a given month for each year, with some evidence of a seasonal trend and a higher proportion of cases reporting symptoms starting in January than would be expected. d.) Shows the proportion of cases notified on a given day for each month, with a much higher proportion of cases reproting symptoms on the first of the month than would be expected. On both the scale of months and years there is some evidence of recall bias, with the first month, or first day, reporting higher proportions of cases than would be expected."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-sympton.png")
```

@@

```{r plot-detection-starttreatdate, fig.cap = "a.) and .b) show notifications over time by date of starting treatment in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases starting treatment in a given month for each year, with some evidence of a seasonal trend. d.) Shows the proportion of cases starting treatment on a given day for each month, with little evidence of between day variation. Data is only shown from 2001 until 2015 and prior to 2001 this variable was not recorded and it is not complete for 2015."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-starttreatdate.png")
```

@@

```{r plot-detection-treatend, fig.cap = "a.) and .b) show notifications over time by date of treatment ending in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases finishing treatment in a given month for each year, with little evidence of a seasonal trend. d.) Shows the proportion of cases finishing treatment on a given day for each month, with a much higher proportion of cases finishing treatment on the first of the month than would be expected. On the scale of months there is some evidence of recall bias, with the first day reporting higher proportions of cases than would be expected. Data is only shown from 2001 until 2015 and prior to 2001 this variable was not recorded and it is not complete for 2015."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-treatend.png")
```

@@

```{r plot-detection-dateofdeath, fig.cap = "a.) and .b) show notifications over time by date of death in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases who died in a given month for each year, with no evidence of a seasonal trend. d.) Shows the proportion of cases who died on a given day for each month, with little evidence of between day variation. Data is only shown from 2001 until 2015 and prior to 2001 this variable was not recorded and it is not complete for 2015."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-dateofdeath.png")
```

>>>>

```{r plot-detection-not, fig.cap = "a.) and b.) show notifications over time by date of notification in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases notified in a given month for each year, with some evidence of a seasonal trend. d.) Shows the proportion of cases notified on a given day for each month, there is little evidence of between day variation in cases notified."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-not.png")
```

@@

```{r plot-detection-sympton, fig.cap = "a.) and b.) show notifications over time by date of symptom onset in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases notified in a given month for each year, with some evidence of a seasonal trend and a higher proportion of cases reporting symptoms starting in January than would be expected. d.) Shows the proportion of cases notified on a given day for each month, with a much higher proportion of cases reproting symptoms on the first of the month than would be expected. On both the scale of months and years there is some evidence of recall bias, with the first month, or first day, reporting higher proportions of cases than would be expected."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-sympton.png")
```

@@

```{r plot-detection-starttreatdate, fig.cap = "a.) and b.) show notifications over time by date of starting treatment in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases starting treatment in a given month for each year, with some evidence of a seasonal trend. d.) Shows the proportion of cases starting treatment on a given day for each month, with little evidence of between day variation. Data is only shown from 2001 until 2015 and prior to 2001 this variable was not recorded and it is not complete for 2015."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-starttreatdate.png")
```

@@

```{r plot-detection-treatend, fig.cap = "a.) and b.) show notifications over time by date of treatment ending in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases finishing treatment in a given month for each year, with little evidence of a seasonal trend. d.) Shows the proportion of cases finishing treatment on a given day for each month, with a much higher proportion of cases finishing treatment on the first of the month than would be expected. On the scale of months there is some evidence of recall bias, with the first day reporting higher proportions of cases than would be expected. Data is only shown from 2001 until 2015 and prior to 2001 this variable was not recorded and it is not complete for 2015."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-treatend.png")
```

@@

```{r plot-detection-dateofdeath, fig.cap = "a.) and b.) show notifications over time by date of death in the ETS, with a.) aggregated by year and  b.) aggregated by month. A trendline has been produced using a locally weighted regression model. Both of these plots show the same overall trend, but b.) contains a large amount of apparent noise. c.) Shows the proportion of cases who died in a given month for each year, with no evidence of a seasonal trend. d.) Shows the proportion of cases who died on a given day for each month, with little evidence of between day variation. Data is only shown from 2001 until 2015 and prior to 2001 this variable was not recorded and it is not complete for 2015."}
knitr::include_graphics("chapters/tb-epi-england/figures/plot-detection-dateofdeath.png")
```
